\huge A Usability Evaluation of Tor Launcher

### 2017-03-21 pets2017-paper/pets2017-paper.tex
wordsmith for style

\subsection{Procedure} 
We ran the experiments in a small room where a monitor, keyboard, and a Windows computer were set up. Using a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment. Before each participant, we ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

We kept the user involved so that they explicitly start a connection to Tor. We chose not to leverage user inputs such as their location, risk, or other preferences. We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.

>>>>

\subsection{Procedure} 
We ran the experiments in a room with a monitor, keyboard, and a Windows computer. On a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer for browser options, and VLC media player~\cite{vlc} for recording the computer screen. Before each participant, we ran a script that simulated E1, E2, or E3 and started recording the computer screen.

@@

We kept the user involved in the configuration so that they explicitly start a connection to Tor (currently, the user needs to click a ``connect'' button before Tor Launcher makes a connection to Tor). 
%We chose not to leverage user inputs such as their location, risk, or other preferences, as this would require additional research on all these options before designing changes incorporating those. 
And although some users in our qualitative study tried to configure unnecessary components, we still also allow all users to choose a manual configuration to give them a chance to connect to Tor securely the first time. 
We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.
